### 2020-10-02 README.Rmd
Works for SCBI!

```{r, eval = run_scbi}
# SCBI
scbi_2013 <- 
  "https://github.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/raw/master/tree_main_census/data/census-csv-files/scbi.stem2.csv" %>% 
  read_csv() %>% 
  select(
    treeID, stemID, sp, quadrat, gx, gy, dbh, 
    date = ExactDate, codes, status
  ) %>%
  mutate(date = mdy(date))

scbi_2018 <-
  "https://github.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/raw/master/tree_main_census/data/census-csv-files/scbi.stem3.csv" %>% 
  read_csv() %>% 
  select(
    treeID, stemID, sp, quadrat, gx, gy, dbh, 
    date = ExactDate, codes, status
  ) %>% 
  mutate(dbh = as.numeric(dbh),
         date = mdy(date)) 
```

@@

scbi_growth_df <- 
  # Merge both censuses and compute growth:
  compute_growth(census_df1, census_df2, id) %>%
  # they are mesuaring in mm while we are measuring in cm!!!
  mutate(growth = growth/10)

@@

```{r, eval = run_scbi}
# SCBI
# Study region boundary polygon
scbi_study_region <- tibble(x = c(0,400,400,0,0), y = c(0,0,640,640,0)) %>% 
  sf_polygon()

@@

```{r, eval = run_scbi}
# SCBI
scbi_cv_grid <- spatialBlock(
  speciesData = scbi_growth_df, theRange = 100, k = 28, yOffset = 0.9999, verbose = FALSE
)

@@

```{r, eval = run_scbi}
# SCBI
tic()
posterior_param_scbi <- focal_vs_comp_scbi %>% 
  fit_bayesian_model(prior_param = NULL, run_shuffle = TRUE)
toc()
```

@@

```{r, eval = run_scbi}
# SCBI
tic()
cv_scbi <- focal_vs_comp_scbi %>%
  run_cv(max_dist = max_dist, cv_grid = scbi_cv_grid) %>%
  right_join(scbi_growth_df, by = c("focal_ID" = "treeID"))
toc()

@@

>>>>

For SCBI we will just look at a 16 ha plot to speed calculations.

```{r, eval = run_scbi}
# SCBI
scbi_2013 <- 
  "https://github.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/raw/master/tree_main_census/data/census-csv-files/scbi.stem2.csv" %>% 
  read_csv() %>% 
  select(
    treeID, stemID, sp, quadrat, gx, gy, dbh, 
    date = ExactDate, codes, status
  ) %>%
  mutate(date = mdy(date)) %>%
  filter(gy <= 400)

scbi_2018 <-
  "https://github.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/raw/master/tree_main_census/data/census-csv-files/scbi.stem3.csv" %>% 
  read_csv() %>% 
  select(
    treeID, stemID, sp, quadrat, gx, gy, dbh, 
    date = ExactDate, codes, status
  ) %>% 
  mutate(dbh = as.numeric(dbh),
         date = mdy(date)) %>%
  filter(gy <= 400)
```

@@

scbi_growth_df <- 
  # Merge both censuses and compute growth:
  compute_growth(census_df1, census_df2, id) %>%
  # they are mesuaring in mm while we are measuring in cm!!!
  mutate(growth = growth/10,
             sp = as.factor(sp))

@@

```{r, eval = run_scbi}
# SCBI
# Study region boundary polygon
scbi_study_region <- 
 #tibble(x = c(0,400,400,0,0), y = c(0,0,640,640,0)) %>% 
  tibble(x = c(0,400,400,0,0), y = c(0,0,400,400,0)) %>% 
  sf_polygon()

@@

```{r, eval = run_scbi}
# SCBI
scbi_cv_grid <- spatialBlock(
  speciesData = scbi_growth_df, theRange = 100, k = 20, yOffset = 0.9999, verbose = FALSE
)

@@

```{r, eval = run_scbi}
# SCBI
tic()
posterior_param_scbi <- focal_vs_comp_scbi %>% 
  fit_bayesian_model(prior_param = NULL, run_shuffle = FALSE)
toc()
```

@@

```{r, eval = FALSE}
# SCBI
tic()
cv_scbi <- focal_vs_comp_scbi %>%
  run_cv(max_dist = max_dist, cv_grid = scbi_cv_grid) %>%
  right_join(scbi_growth_df, by = c("focal_ID" = "treeID"))
toc()

@@

** SCBI

```{r, eval = run_bw}
posterior_plots_scbi <- plot_posterior_parameters(
  posterior_param = posterior_param_scbi,
  sp_to_plot = c("libe", "caca", "astr", "litu", "havi", "cagl", "cato")
)
```

```{r, eval = run_bw}
posterior_plots_scbi[["lambda"]]
```
